Object-based Auditory Scenes Similarity and Classification Using Scattering Features

### 2016-07-07 paper/structureScene.tex
raw edit of beginning of section 2

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
This paper introduces a 
\end{abstract}

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
Acoustic scene classification, segmentation.
\end{IEEEkeywords}

@@

Despite the differences, the following question is valid both for the above cited future application and the acoustic scene classification (ASC). How can we efficiently and effectively process large amount of audio data using representations that are both compact, generic in their design and with a large application range ?

The research described in this paper tackles that question by demonstrating the usefulness of two main contributions: 1) the use of the scattering transform allows us to extract discriminative features with almost no parameter optimization and 2) object-based modeling of the acoustic scene based on individual unsupervised clustering of each acoustic scene  allows us to effectively focus the description on areas of interest. Those contributions are extensively described, respectively in Section \ref{sec:scattering} and \ref{sec:object} and evaluated both in an unsupervised setting, \textit{i.e.} acoustic scene similarity (ASS) and in a supervised setting, \textit{i.e.}  acoustic scene classification (ASC), respectively in Section \ref{sec:similarity} and Section \ref{sec:classification}.

paper

In this paper, we investigate the potential of a new unsupervised segmentation paradigm that allows us to

This data has to be processed

Environment sound

If available, the complete description of the scene in terms of event occurences is powerful enough to reliably predict high level cognitive classes, \textit{i.e.} the presence of birds are strong pleasantness indicators and very likely to be heard in parks in urban areas.

\section{Previous work}

\gl{bag of frame approach:} \cite{aucouturier2007bag}: bag of frame approach. \cite{lagrange:hal-01082501}: why the bag of frame approach does no work. \\

@@

@@

GL

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Object-based Auditory Scenes Similarity and Classification Using Scattering Features}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
This paper introduces a generic hierarchical modeling of acoustic scenes using time/frequency scattering features for time spans below the second and object-based segmentation for larger time spans that effectiely model the scene with almost no requirement for optimization. Application of the proposed approach to the acoustic scene similarity and acoustic scene classification tasks demonstrates its potential.

More precisely, the proposed approach achieves 
\end{abstract}

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
Acoustic scene classification, acoustic scene segmentation.
\end{IEEEkeywords}

@@

Despite the differences, the following question is valid both for the above cited future application and the acoustic scene classification (ASC) task. How can we efficiently and effectively process large amount of audio data using representations that are both compact, generic in their design and with a large application range ?

The research described in this paper tackles that question by demonstrating the usefulness of two main contributions: 1) the use of the scattering transform allows us to extract discriminative features with almost no parameter optimization and 2) object-based modeling of the acoustic scene based on individual unsupervised clustering of each acoustic scene  allows us to effectively focus the description on areas of interest. After studying the state of the art in the field of acoustic scene modeling in Section \ref{sec:soa}, those contributions are extensively described, respectively in Section \ref{sec:scattering} and \ref{sec:object} and evaluated both in an unsupervised setting, \textit{i.e.} acoustic scene similarity (ASS) and in a supervised setting, \textit{i.e.}  acoustic scene classification (ASC), respectively in Section \ref{sec:similarity} and Section \ref{sec:classification}.

\section{Previous work} \label{sec:soa}

As stated in the introduction, the field of eco-acoustics is relatively young, but significant works are worth mentioning. One avenue of research issued from bio acoustic studies, consider the audio stream as a set of events produced animals, and is processed to retrieve the precise species that produced the sound and potentially the type of vocalization in order to predict some behavior of the animal under study \cite{dan}. Another, more recent, avenue of research, process the audio stream in an holistic manner in order to infer large time-scale properties of the bio-acoustic scene for example to estimate which part of the stream need to be analyzed in details, \textit{i.e.} by a human \cite{australians}.

The same dichotomy applies for the field of audio scene analysis, where the interest can be whether 1) to isolate and identify precise events, \textit{i.e.} acoustic event detection (AED) or 2) to predict global attributes assigned to large time spans of audio, \textit{i.e.} ASC. For the latter, most state-of-the-art systems roughly follow the bag of frame approach (BOF) initiated in \cite{aucouturier2007bag} where the audio is modelled as high level statistics comptued from a set of local features. Even though this approach as the advantage of high genericity and follows some evidence found by psycho perception research \cite{macdermott}, for the specific implementation with gaussian mixture models (GMMs) of Mel-frequency cepstral coefficients (MFCCs) it is demonstrated to be equivalent to  \cite{lagrange:hal-01082501}.

citer papier event based de l'intro de jj

 there is evidence that modelling the scene as a set of events allows us to predict high level semantic information such as pleasantness

Eventhough the precise list of events that occur in a given time is unachievable to get even for trained human, research shows that using only a few events, so called markers \cite{} is enough to reliably predict high level attributes. For example, the presence of a few bird calls in a smooth traffic hubhub is likely to be tagged by humans as a park scene in urban areas \gl{citations ?}.

@@

If available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high level cognitive classes, \textit{i.e.} the presence of birds are strong pleasantness indicators and very likely to be heard in parks in urban areas.

@@
